Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-11 paper/ms.tex
Add list of conclusions

\begin{itemize}
\item

>>>>

\begin{itemize}
\item We demonstrated that an inaccuracy in the Galactocentric coordinate
system induces time evolution in the {\em observed} actions
(Figures~\ref{fig:cartoon}\&\ref{fig:one_orbit_wrong_ref}).

\item We interpret this time evolution as an error in the computed action
(Figure~\ref{fig:many_orbit_wrong_ref}). We focused on the effect that an
inaccuracy in the midplane has on the vertical action $J_z$. We found that in
order for there to be a $100\%$ error in $J_z$ (as defined by the middle
$90\uth$ percentile) one needs a midplane error of $\sim30\,\pc$ and
$\sim225\,\pc$ for a typical thin and thick disk orbit, respectively. The
fractional error is significantly less for halo orbits.

\item We pointed out that the error distribution of the actions induced by a
coordinate system error is very non-Gaussian. The distribution is bimodal with
{\em neither of the modes peaking at the true value}. As a result, error
propagation is very involved when considering actions.

\item We proposed that dynamical modelling across large regions of the disk is
susceptible to this type of error, since the assumption that our local
Galactic midplane is the global Galactic midplane is not true {\em a priori}.

\item To demonstrate the previous point, we measured the local Galactic
midplane along the Solar circle in three different high-resolution, zoom-in
simulations of Milky Way mass galaxies from the FIRE collaboration. We found
that the midplane varies by $\sim185, 162, 84\,\pc$ (middle $90\%$) for the
three galaxies we considered (m12i, m12f, and m12m, respectively).
